Automated verification of stand-alone solar photovoltaic systems

### 2018-11-13 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r2.tex
IEEE thesaurus

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
With declining costs and increasing performance, the deployment of renewable energy in \textcolor{red}{What is the difference between off-grid and stand-lone? In the title you mention stand-alone and in the abstract you mention off-grid... please keep a standard...} off-grid systems is growing in both developed and developing countries, with particular emphasis on solar photovoltaic systems. Electrification of rural areas can improve the education standard, health conditions, and also the life of that population. In addition, depending on the country geography, using renewable energy sources in off-grid mode is a feasible solution if compared to a grid extension. \textcolor{red}{half of your abstract is about the context... you should reduce it a bit further..} Tools to aid the design and validation of rural electrification projects are available; however, there is no software that applies formal verification to evaluate rural electrification projects. This paper aims to apply an automated verification method to mathematical models of a solar photovoltaic system to validate its design from a formal verification perspective. Data from practical application of solar systems prove the results obtained by the proposed approach, where specific conditions that lead to failures in a photovoltaic solar system are only detected with the verification tool if compared to a simulation tools.
%Experimental results show that the proposed approach can find situations where the sized solar photovoltaic system fails to meet the requirements demanded to electrify a house, and that simulation made with commercial tools can not find the same failure. \textcolor{red}{Data from practical application of solar systems prove the results obtained by the proposed approach... this last sentence should be stronger to emphasise your main contribution... maybe you could update this after obtaining the experimental results...}
\end{abstract}

>>>>

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
With declining costs and increasing performance, the deployment of renewable energy systems is growing in both developed and developing countries, with particular emphasis on stand-alone solar photovoltaic systems where grid extension is not feasible. Tools to evaluate the design and validate those electrification projects are available; however, those tools are based on simulation that do not cover all the aspects of the design space. Automated verification using formal methods, in the other hand, is proven to be a reference technique to program verification. However, any kind of system can be verified by formal method, including the most complexes. At this paper, each component of a stand-alone solar photovoltaic system, as solar panel, charge controller, battery, inverter, and electric load, were coded as a mathematical model, and a algorithm using automated verification was created in order to validate its design from a formal verification perspective. Case studies, from real photovoltaic systems deployed in five different sites, ranging from 700 W to 1,200 W, were used to evaluate the proposed technique, always comparing the results with the specialized simulation tool HOMER Pro. Data from practical application prove the results obtained by the proposed approach, where specific conditions that lead to failures in a photovoltaic solar system are only detected with the verification tool.
%Experimental results show that the proposed approach can find situations where the sized solar photovoltaic system fails to meet the requirements demanded to electrify a house, and that simulation made with commercial tools can not find the same failure. \textcolor{red}{Data from practical application of solar systems prove the results obtained by the proposed approach... this last sentence should be stronger to emphasise your main contribution... maybe you could update this after obtaining the experimental results...}
\end{abstract}
